Review of Assigned Readings

### 2017-12-28 documentation/documentation.tex
adjusted spelling and punctuation mistakes

\subsubsection{Hardware Setup}
As explained in the previous section the twitter API was used to filter tweets in realtime based on the buzzword "bitcoin". The Python program was running for seven days without interruption on a Raspberry Pi 2 (RPI) which was accessed with a Secure Shell (SSH) connection. This approach allowed us to ensure a continuous data stream while being able to access the program output regardless anywhere and anytime. Furthermore due to a low energy consumption of the RPI the method is also the most cost efficient one compared to a personal computer or NAS Server. The following section describes the different steps that have been taken in order to setup the RPI 2, SSH, Git and Python3.\newline

>>>>

\subsubsection{Hardware Setup}
As explained in the previous section the twitter API was used to filter tweets in real time based on the buzzword "bitcoin". The Python program was running for seven days without interruption on a Raspberry Pi 2 (RPI) which was accessed with a Secure Shell (SSH) connection. This approach allowed us to ensure a continuous data stream while being able to access the program output regardless of time and location. Furthermore, due to a low energy consumption of the RPI the method is also the most cost efficient one compared to a personal computer or NAS Server. The following section describes the different steps that have been taken in order to setup the RPI 2, SSH, Git and Python3.\newline
